%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[colorlinks,linkcolor=blue]{hyperref}
\usepackage[left=0.7in,top=0.6in,right=0.7in,bottom=0.6in]{geometry} % Document margins
% \usepackage{enumitem}
% \setitemize[1]{itemsep=-4pt,partopsep=0pt,parsep=\parskip,topsep=-4pt}

\name{Shangzhe Di} % Your name
\address{(86)15652587063 \\ \href{mailto:shangzhe.di@gmail.com}{shangzhe.di@gmail.com}} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Beihang University\,(BUAA)}{Sep 2016 - Jul 2020}{B.E in Software Engineering}{Beijing}
    \item Overall GPA: 90.05/100 $\diamond$ Major GPA: 93.79/100 $\diamond$ Ranking: 11/157
    \item First Prize Scholarship for Academic Performance (Top 8\%) \hfill  Nov 2019
    \item Special Prize Scholarship for Academic Performance (Top 3\%) \hfill  Nov 2018 
\end{rSubsection}
\vspace{-0.6em}

%------------------------------------------------
\smallskip
\begin{rSubsection}{Technical University of Munich\,(TUM)}{Apr 2019 - Aug 2019}{Exchange program, Informatics Department}{Munich}
    \item China Scholarship Council\,(CSC) Scholarship \hfill Apr 2019
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Research EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{Flow-based Virtual Try-On System}{Oct 2019 - Present}{Research Intern, Kwai Co.,Ltd., Supervisor: Yilin Guo}{Beijing}
\item Work on building an appearance-flow based generation system for virtual try-on.
\item Improve cloth deformation quality by introducing DensePose to provide 3D information.

\end{rSubsection}

\begin{rSubsection}{Landmark-Free Facial Motion Transfer to VTubers}{May 2019 - Jul 2019}{Research Assistant, Visual Computing Group, TUM}{Munich}
\item Design an efficient network to estimate 3DMM pose and expression parameters from RGB video frames, which are then used to control the facial movements of VTubers.
\item Enhance accuracy at large angles and computational efficiency towards landmark-based methods.
\end{rSubsection}

\end{rSection}



\begin{rSection}{Teaching Experience}

\begin{rSubsection}{Introduction to Computer Science}{Sep 2019 - Dec 2019}{Beihang University, Supervisor: Prof.\,Yunxiang Lv}{Beijing}
\item Hold Python tutorials, programming exercises, and office hours.

\end{rSubsection}

\begin{rSubsection}{AI Seminar}{Sep 2018 - Present}{Beihang University, Supervisor: Prof.\,Hongyi Li}{Beijing}
\item Hold regular lectures on machine learning and deep learning.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Coursework Project}

\begin{rSubsection}{Conference Management Weixin Mini Program}{Jul 2019 - Sep 2019}{}{}
\item Develop a mini-program based on Flask and Weixin platform, making it easy and efficient for everyone to create and manage meetings.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{PL$\backslash$0 Compiler}{Oct 2018 - Dec 2018}{}{}
\item Implement the PL$\backslash$0 compiler using Python and the front-end based on the Java Sprint framework.
\end{rSubsection}

%------------------------------------------------

% \begin{rSubsection}{Integration of Campus Information app}{Jan 2018 - Mar 2018}{}{}
% \item Implement the web server based on Python Flask framework. 
% \item With this app, users can loop up curriculum or grades data, post on Campus Moments, and trade on the flea market, etc.
% \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, C++, Java, HTML, JavaScript \\
Platforms/Frameworks & Numpy, PyTorch, Scipy, Ceres, Flask, Sprint
% English & TOEFL 107, GRE 325
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
